Geometric variational problems

### 2020-11-16 NSF2020/Description/broaderimpacts.tex
added serial comma
Update broaderimpacts.tex

This project aims to advance the mathematical modeling of collective 
dynamics of amphiphilic particles. The simulations use a new, yet intuitive,
approach that can reach important and complex systems that are presently out of 
reach in computational material science. These complex systems include 
fusion and fission of amphiphilic bilayer membranes and optimal shape design
in metamaterials. The development of three-dimensional 
models describing colloidal systems could be transformative in biomedicine
and material science. The research draws from expertise in scientific 
computing, physics of fluids and mathematics. The mathematical component 
incorporates leading techniques from geometric analysis and gives deep insight 
into fundamental material science. The project offers undergraduates 
in a socially impactful manner the opportunity to do research and train 
with graduate and postdoctoral personnel. It incorporates research in the 
classroom, and with its combination of mathematical modeling, analysis, 
and scientific computing, the project highlights the importance of 
mathematics and computation to all areas of science and engineering.

@@

There are two ways the proposal will meaningfully engage the community.
To be more impactful, students from the Bronx High School of Science (PI
RR) and Newark Science Park High School (PI YNY) will be encouraged to
join the research team. PI BQ will work with undergraduate and high
school students through the Undergraduate Research Opportunity Program
and Young Scholar's Program, as he has done in the past. Secondly, the
PIs will prioritize students who would most benefit from the grant
activity. We specifically target students whose socio-economic
background prevents them from participating in out-of-state research
experiences.

>>>>

This project aims to advance the mathematical modeling of collective 
dynamics of amphiphilic particles. The simulations use a new, yet intuitive,
approach that can reach important and complex systems that are presently out of 
reach in computational material science. These complex systems include 
fusion and fission of amphiphilic bilayer membranes and optimal shape design
in metamaterials. The development of three-dimensional 
models describing colloidal systems could be transformative in biomedicine
and material science. The research draws from expertise in scientific 
computing, physics of fluids, and mathematics. The mathematical component 
incorporates leading techniques from geometric analysis and gives deep insight 
into fundamental material science. The project offers undergraduates 
in a socially impactful manner the opportunity to do research and train 
with graduate and postdoctoral personnel. It incorporates research in the 
classroom, and with its combination of mathematical modeling, analysis, 
and scientific computing, the project highlights the importance of 
mathematics and computation to all areas of science and engineering.

@@

There are two ways the proposal will meaningfully engage the community.
To be more impactful, students from the Bronx High School of Science (PI
RR) and Newark Science Park High School (PI YNY) will be encouraged to
join the research team. PI BQ will work with undergraduate and high
school students through the Undergraduate Research Opportunity Program
and Young Scholar's Program, as he has done in the past. Secondly, the
PIs will prioritize students who would most benefit from the grant
activity. These include students from underrepresented groups,
and we specifically target students whose socio-economic
background prevents them from participating in out-of-state research
experiences.
